When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-14 paper/paper.tex
Ref VF2 when it first appears (review 1)

What about other random graph models? In \cref{section:regular} we see that graphs where every vertex
has the same degree (known as $k$-regular) exhibit very similar characteristics.  However, when
labels on vertices are introduced (as is commonly seen in real-world applications and in graph
database systems), richer behaviour emerges, particularly when moving away from a uniform labelling
scheme, and the popular VF2 algorithm behaves much worse than two more recent
constraint-based algorithms in certain cases. In \cref{section:labelled} we take a close look at
these cases, and argue that they \emph{should} be easy to solve.

>>>>

What about other random graph models? In \cref{section:regular} we see that graphs where every vertex
has the same degree (known as $k$-regular) exhibit very similar characteristics.  However, when
labels on vertices are introduced (as is commonly seen in real-world applications and in graph
database systems), richer behaviour emerges, particularly when moving away from a uniform labelling
scheme, and the popular VF2 algorithm \citep{DBLP:journals/pami/CordellaFSV04} behaves much worse
than two more recent constraint-based algorithms in certain cases. In \cref{section:labelled} we
take a close look at these cases, and argue that they \emph{should} be easy to solve.
